An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps

### 2020-01-14 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
election example, not happy with it

```{r liver-geo}
knitr::include_graphics("figures/aus_liver_m.png")
```

```{r liver-hex}
knitr::include_graphics("figures/aus_liver_m_hex.png")
```

@@

The concept of tile mapping with both hexagons and squares is not unfamiliar in practice. In fact there are many prominent news sites that utilise these techniques, these include [@NPR], [@FiveThirtyEight], [@WSJ], [@WP]. 
A common applicate of the hexagon tile map is election mapping for United States of America.

XXX Code from web site, and a couple of paragraphs of explanation

@@

@@

Alternative maps highlight the value of the statistics across the geographic units. Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area. This acknowledges that the amount of residents can be different but recognises that each population area is equally important. The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections. This map algorithm is implemented in the @sugarbag package written for @R.
The \pkg{sugarbag} package creates tesselated hexagon tilegrams. The Australian application preserves the spatial relationships, emphasising capital cities. The hexagon tile map is a visualisation solution that highlights spatial distributions.

@@

The code for sugarbag [@sugarbag] can be found on [CRAN](https://cran.r-project.org/web/packages/sugarbag/index.html), along with vignettes on installation and usage.

>>>>

```{r liver-geo, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"                             }
knitr::include_graphics("figures/aus_liver_m.png")
```

```{r liver-hex, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"}
knitr::include_graphics("figures/aus_liver_m_hex.png")
```

@@

The concept of tile mapping with both hexagons and squares is not unfamiliar in practice.
A common application of the hexagon tile map is election mapping for United States of America, there are many prominent news sites that utilise these techniques [@NPR], [@FiveThirtyEight], [@WSJ], [@WP]. 
To apply hexagon tile mapping to election mapping Australia using \code{R}, the \pkg{sugarbag} package provides Australian election data and the Australian Electoral Commission provides electoral boundaries for 2019 [@AEC19].

```{r aec-packages}
library(sugarbag)
library(eechidna)

# First Preference votes in 2019
data(sugarbag::fp19)
# Electoral Boundaries
nat_data19 <- nat_data_download(2019)
```

The centroids are derived from the National Electoral data for 2019 provided in the \{eechidna} package.

```{r aec-centroids}
centroids <- nat_data19 %>%
  select(Elect_div = elect_div, longitude = long_c, latitude = lat_c)
```

The hexagon grid for allocation is created using the set of electorate centroids.

```{r aec-grid}
# Create a grid of hexagons to allocate centroids
grid <- create_grid(centroids = centroids, hex_size = 0.9, buffer_dist = 10)
```

The centroids and the grid can be passed to the \code{allocate} function.

```{r allocate}
# Allocate the centroids to the hexagon grid
# We have the same amount of rows, as individual regions
hex_allocated <- allocate(centroids = centroids,
  sf_id = "Elect_div",
  hex_grid = grid,
  hex_size = 0.9, # same size used in create_grid
  hex_filter = 10,
  use_neighbours = ELB,
  focal_points = capital_cities,
  width = 30, verbose = TRUE) # same column used in create_centroids
```

To display hexagons on a map, \code{fortify_hexagon} takes the center of the hexagon and finds the 6 points needed to create a hexagon shape.

For animations to move between geography and hexagons the \code{sf_id} must match, there also needs to be an identifier to separate the states to animate between for \code{gganimate}.

```{r data}
# When plotting, the polygons are needed, rather than single centroid points.
# We can find 6 points, and then convert them into an sf geometry object
hex <- hex_allocated %>%
  fortify_hexagon(hex_size = 0.9, sf_id = "Elect_div") %>%
  select(Elect_div, long, lat) %>% 
  sf::st_as_sf(coords = c("long", "lat"), crs = 4283) %>%
  group_by(Elect_div) %>% 
  summarise(do_union = FALSE) %>%
  st_cast("POLYGON") %>%
  st_cast("MULTIPOLYGON") %>% 
  left_join(st_drop_geometry(nat_data19), ., by = "Elect_div")

anim_aus <- bind_rows("Hex." = hex, "Choro." = ELB19, .id = "polygon_type") %>% st_as_sf()

# Join election data from 2016
fp_maps <- fp19 %>% 
  filter(Elected == "Y") %>% 
  select(Elect_div = DivisionNm, PartyAb, PartyNm, TotalVotes) %>% 
  left_join(anim_aus, by = "Elect_div")

```

Here we show the two sets of areas they can be plotted separately using `geom_facet`.

```{r plot_facet, dpi = 300}
auscolours <- c(
  "ALP" = "#DE3533",
  "LNP" = "#080CAB",
  "KAP" = "#b50204",
  "GRN" = "#10C25B",
  "XEN" = "#ff6300",
  "LNP" = "#0047AB",
  "LP" = "#0047AB",
  "NP" = "#006644",
  "IND" = "#307560")

ggplot(fp_maps %>% filter(polygon_type == "Hex."), 
  aes(geometry = geometry, fill = PartyAb)) +
  scale_fill_manual(values = auscolours) +
  geom_sf(fill = "white", data = absmapsdata::state2016) +
  geom_sf() +
  theme_void()

ggplot(fp_maps %>% filter(polygon_type == "Choro."), 
  aes(geometry = geometry, fill = PartyAb)) +
  scale_fill_manual(values = auscolours) +
  geom_sf(fill = "white", data = absmapsdata::state2016) +
  geom_sf() +
  theme_void()
```

We can move between the two plots using the \code{transition_states} function from the \code{gganimate} package.

@@

```{r}
anim <- anim_aus %>% 
  ggplot(aes(x=long, y=lat, group = interaction(elect_div))) +
  geom_polygon(aes(x=long, y=lat, group = group),fill = "grey", alpha = 0.3, data= nat_map16) +
  geom_polygon(aes(fill = PartyAb)) + 
  coord_equal() + 
  theme_void() +
  scale_fill_manual(values = auscolours) +
  guides(fill = guide_legend(title = NULL)) + 
  theme(legend.position = "bottom") +
  transition_states(poly_type)
animate(anim, duration = 6, nframes = 60)
```

@@

Alternative maps highlight the value of the statistics across the geographic units. Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area. This acknowledges that the amount of residents can be different but recognises that each population area is equally important. The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections. This map algorithm is implemented in the \pkg{sugarbag} @sugarbag package written for \code{R} @R.
The \pkg{sugarbag} package creates tesselated hexagon tilegrams. The Australian application preserves the spatial relationships, emphasising capital cities. The hexagon tile map is a visualisation solution that highlights spatial distributions.

@@

The code for \pkg{sugarbag} [@sugarbag] can be found on [CRAN](https://cran.r-project.org/web/packages/sugarbag/index.html), along with vignettes on installation and usage.

Australian Electoral Data can be found in the \pkg{eechidna} package for R.

### 2020-01-14 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
election example, not happy with it

\begin{CodeInput}
R> knitr::include_graphics("figures/aus_liver_m.png")
\end{CodeInput}

\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m} \end{center}

\begin{CodeInput}
R> knitr::include_graphics("figures/aus_liver_m_hex.png")
\end{CodeInput}

\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m_hex} \end{center}

@@

Alternative maps highlight the value of the statistics across the
geographic units. Alternative mapping methods allow increased
understanding of the spatial distribution of a variable across the
population, by fairly representing each administrative area. This
acknowledges that the amount of residents can be different but
recognises that each population area is equally important. The solution
to this visualisation problem has equally sized areas, with
neighbourhood boundary connections. This map algorithm is implemented in
the \citet{sugarbag} package written for \citet{R}. The \pkg{sugarbag}
package creates tesselated hexagon tilegrams. The Australian application
preserves the spatial relationships, emphasising capital cities. The
hexagon tile map is a visualisation solution that highlights spatial
distributions.

@@

The code for sugarbag \citep{sugarbag} can be found on
\href{https://cran.r-project.org/web/packages/sugarbag/index.html}{CRAN},
along with vignettes on installation and usage.

>>>>

\begin{figure}

{\centering \includegraphics[width=0.6\linewidth]{figures/aus_liver_m}

\caption[A choropleth map of the Statistical Areas of Australia at Level 2]{A choropleth map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)}\label{fig:liver-geo}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.6\linewidth]{figures/aus_liver_m_hex}

\caption[A hexagon tile map of the Statistical Areas of Australia at Level 2]{A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)}\label{fig:liver-hex}
\end{figure}

@@

Alternative maps highlight the value of the statistics across the
geographic units. Alternative mapping methods allow increased
understanding of the spatial distribution of a variable across the
population, by fairly representing each administrative area. This
acknowledges that the amount of residents can be different but
recognises that each population area is equally important. The solution
to this visualisation problem has equally sized areas, with
neighbourhood boundary connections. This map algorithm is implemented in
the \pkg{sugarbag} \citet{sugarbag} package written for \code{R}
\citet{R}. The \pkg{sugarbag} package creates tesselated hexagon
tilegrams. The Australian application preserves the spatial
relationships, emphasising capital cities. The hexagon tile map is a
visualisation solution that highlights spatial distributions.

@@

The code for \pkg{sugarbag} \citep{sugarbag} can be found on
\href{https://cran.r-project.org/web/packages/sugarbag/index.html}{CRAN},
along with vignettes on installation and usage.
